### 2021-07-24 paper.tex
All architectures added.
Methodology is complete. Implementation needs to be done.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

@@

	VGG 16 is is a significantly more accurate ConvNet architecture, which not
	only achieve state-of-the-art accuracy on ILSVRC classification and
	localisation tasks, but are also applicable to other image recognition
	datasets, where they achieve excellent performance even when used as a part
	of a relatively simple pipelines (e.g. deep features classified by a linear
	SVM without fine-tuning).

@@

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.5\linewidth]{imgs/vgg16_arch.png}
		\caption{VGG Architecture}%
		\label{fig:vgg_arch}
	\end{figure}

@@

	All hidden layers are equipped with the rectification (ReLU) non-linearity.
	We note that none of our networks (except for one) contain Local Response
	Normalisation (LRN) normalisation: as will be shown in Sect. 4, such
	normalisation does not improve the performance on the ILSVRC dataset, but
	leads to increased memory con- sumption and computation time. Where
	applicable, the parameters for the LRN layer are those of.

@@

	The ConvNet configurations, evaluated in this paper, are outlined in Table
	1, one per column. In the following we will refer to the nets by their names
	(A–E).  All configurations follow the generic design presented in
	Section~\ref{sssec:vgg arch} and differ only in the depth: from 11 weight
	layers in the network A (8 conv. and 3 FC layers) to 19 weight layers in the
	network E (16 conv. and 3 FC layers). The width of conv. layers (the number
	of channels) is rather small, starting from 64 in the first layer and then
	increasing by a factor of 2 after each max-pooling layer, until it reaches
	512.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.8\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}

@@

\usepackage{wrapfig}

@@

	VGG 16 is is a significantly more accurate ConvNet architecture, which not
	only achieve state-of-the-art accuracy on ILSVRC classification and
	localisation tasks, but are also applicable to other image recognition
	datasets, where they achieve excellent performance even when used as a part
	of a relatively simple pipelines (e.g. deep features classified by a linear
	SVM without fine-tuning) \cite[1]{simonyan2015deep}.

@@

	\begin{wrapfigure}{r}{0.5\textwidth}
		\begin{center}
			\includegraphics[ width=0.5\textwidth ]{imgs/vgg16_arch.png}
		\end{center}
		\caption{VGG Architecture}
	\end{wrapfigure}

@@

@@

	All hidden layers are equipped with the rectification (ReLU) non-linearity.
	We note that none of our networks (except for one) contain Local Response
	Normalisation (LRN) normalisation: as will be shown in Sect. 4, such
	normalisation does not improve the performance on the ILSVRC dataset, but
	leads to increased memory con- sumption and computation time.
	\cite[1]{simonyan2015deep}

@@

	The ConvNet configurations, evaluated in this paper, are outlined in
	Figure~\ref{fig:vgg16_conf}, one per column. In the following we will refer
	to the nets by their names (A–E).  All configurations follow the generic
	design presented in Section~\ref{sssec:vgg arch} and differ only in the
	depth: from 11 weight layers in the network A (8 conv. and 3 FC layers) to
	19 weight layers in the network E (16 conv. and 3 FC layers). The width of
	conv. layers (the number of channels) is rather small, starting from 64 in
	the first layer and then increasing by a factor of 2 after each max-pooling
	layer, until it reaches 512.
	\cite[3]{simonyan2015deep}

	\begin{figure}[h]
		\centering
		\includegraphics[width=\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

	\subsection{ResNet 50}%
	\label{sub:ResNet 50}

	\subsubsection{Residual Learning}

	\begin{wrapfigure}{r}{0.5\textwidth}
		\begin{center}
			\includegraphics[ width=0.5\textwidth ]{imgs/resnet_arch2.png}
		\end{center}
		\caption{Resnet Architecture}
	\end{wrapfigure}

	Let us consider $H(x)$ as an underlying mapping to be fit by a few stacked
	layers (not necessarily the entire net), with $x$ denoting the inputs to the
	first of these layers. If one hypothesizes that multiple nonlinear layers
	can asymptotically approximate complicated functions, then it is equivalent
	to hypothesize that they can asymptotically approximate the residual
	functions, i.e., $H(x) - x$ (assuming that the input and output are of the
	same dimensions). So rather than expect stacked layers to approximate $H(x)$
	, we explicitly let these layers approximate a residual function
	\begin{equation}
		F(x) = H(x) - x
	\end{equation}
	The original function thus becomes $F(x) + x$. Although both forms should be
	able to asymptot- ically approximate the desired functions (as
	hypothesized), the ease of learning might be different \cite[3]{he2015deep}.

	\subsubsection{Network Architecture}

	The plain/residual network was tested as follows:

	\textbf{Plain Network}

	Our plain baselines are mainly inspired by the philosophy of VGG nets.  The
	convolutional layers mostly have 3×3 filters and follow two simple design
	rules:

	\begin{enumerate}
		\item for the same output feature map size, the layers have the same
			number of filters
		\item if the feature map size is halved, the number of filters is
			doubled so as to preserve the time complexity per layer.
	\end{enumerate}

	We perform downsampling directly by convolutional layers that have a stride
	of 2. The network ends with a global average pooling layer and a 1000-way
	fully-connected layer with softmax. The total number of weighted layers are
	34.  It is worth noticing that our model has fewer filters and lower
	complexity than VGG nets. Our 34-layer baseline has 3.6 billion FLOPs
	(multiply-adds), which is only 18\% of VGG-19 (19.6 billion FLOPs)
	\cite[3]{he2015deep} .

	\textbf{Residual Network}
	Based on the above plain network, we insert shortcut connections which turn
	the network into its counterpart residual version. The identity shortcuts
	can be directly used when the input and output are of the same dimensions.
	When the dimensions increase, we consider two options:
	\begin{enumerate}
		\item The shortcut still performs identity mapping, with extra zero
			entries padded for increasing dimensions. This option introduces no
			extra parameter
		\item The projection shortcut is used to match dimensions (done by 1×1
			convolutions).
	\end{enumerate}
	For both options, when the shortcuts go across feature maps of two sizes,
	they are performed with a stride of 2 \cite[4]{he2015deep} .

	\begin{figure}[h]
		\centering
		\includegraphics[width=\linewidth]{imgs/resnet_arch.png}
		\caption{resnet50 configuration}%
		\label{fig:resnet conf}
	\end{figure}
